Biotic invasions fuck with the manageability of pollination networks

### 2017-02-23 paper/supp_info_2.Rmd
Cache slow R chunks

```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Frequency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**. Rows correspond to study sites."}
sites <- net_prop %>% dplyr::arrange(study, site, inv) %$% site %>% unique()
threshold_data <- d_sp %>%
			dplyr::filter(scaled == FALSE, 
										study != "ballantyne", 
										type == "asymmetry") %>%
			dplyr::mutate(f_s = d_freq / n_matchings, 
										f_d = (n_matchings - m_freq) / n_matchings, 
										site = factor(site, sites), 
										site_num = as.numeric(site)) %>%
			dplyr::group_by(net_name, threshold, species) %>%
			dplyr::summarise(f_s = mean(f_s),
											 f_d = mean(f_d), 
											 site = dplyr::first(site),
											 site_num = dplyr::first(site_num),
											 inv = dplyr::first(inv)) %>%
			dplyr::group_by() %>%
			dplyr::mutate(site_num = site_num -1, # to account for ballantynes
										inv = plyr::mapvalues(inv, c(T, F), 
																					c("invaded", "uninvaded")))
# not finished note
note <- data.frame(site_num = 8, inv = "invaded", text = "results not available")

@@

```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a superior node ($f_D$) as a function of the matching weight threshold**. Rows correspond to study sites."}
p[[2]] + ylab(expression(f[D]))

>>>>

```{r fig-f-s-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap="**Frequency with which a species was classified as a superior node ($f_S$) as a function of the matching weight threshold**. Rows correspond to study sites.", cache = T}
sites <- net_prop %>% dplyr::arrange(study, site, inv) %$% site %>% unique()
threshold_data <- d_sp %>%
			dplyr::filter(scaled == FALSE, 
										study != "ballantyne", 
										type == "asymmetry") %>%
			dplyr::mutate(f_s = d_freq / n_matchings, 
										f_d = (n_matchings - m_freq) / n_matchings, 
										site = factor(site, sites), 
										site_num = as.numeric(site)) %>%
			dplyr::group_by(net_name, threshold, species) %>%
			dplyr::summarise(f_s = mean(f_s),
											 f_d = mean(f_d), 
											 site = dplyr::first(site),
											 site_num = dplyr::first(site_num),
											 inv = dplyr::first(inv)) %>%
			dplyr::group_by() %>%
			dplyr::mutate(site_num = site_num -1, # to account for ballantynes
										inv = plyr::mapvalues(inv, c(T, F), 
																					c("invaded", "uninvaded")))
# not finished note
note <- data.frame(site_num = 8, inv = "invaded", text = "results not available")

@@

```{r fig-f-d-rankings, echo = F, message = F, warning = F, fig.width = 6.2, fig.height = 9, results = "hide", fig.cap= "**Frequency with which a species was classified as a superior node ($f_D$) as a function of the matching weight threshold**. Rows correspond to study sites.", cache = T}
p[[2]] + ylab(expression(f[D]))
